---
title: "The CLT"
author: "Rachel Polack"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
options(digits = 1)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

In the graph above it is not unimodal, but in fact bimodal, seeing that there are two peaks instead of just a singular peak. Both peaks are not of the same size. The sample mean is `r mean(my1000)` and the standard deviation is `r sd(my1000)`. 

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The plot above is not unimodal, but instead trimodal due to having three peaks instead of a singular peak. All three peaks are not of the same size. The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`.

Do this again for 4 random samples

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`.


Then again for 9 random samples

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`.


then 16 random samples

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`.


finally for 36 random samples.

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`.


Write a summary paragraph describing what you observed and how it relates to the central limit theorem.